On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-06-09 reports/confidential/insecureport.tex
mark white paper as confidential

\fix{mr}{this proof needs to be done}
\begin{proof}
In Appendix~\ref{app:commproof}, we report the proof which is exhaustive on all
possible combinations.  In the following we report only the excluded cases and
assume the other to be strightforwad (as a proof sketch).
\begin{enumerate}
	\item \emph{input secure port} and 
		\begin{enumerate}
			\item \emph{output drop port} ($s\sdcom r$), 
			\item \emph{output insertion port} ($s\sicom r$), 
			\item \emph{output injection port} ($s\sjcom r$), 
			\item \emph{output selective drop port} ($s\ssdcom r$), 
			\item \emph{output selective insertion port} ($s\ssicom r$), 
			\item \emph{output selective injection port} ($s\ssjcom r$), 
		\end{enumerate}
	\item \emph{input drop port} (all the input-assertions are dropped) and 
		\begin{enumerate}
			\item \emph{output drop port} ($s\ddcom r$), this
				configuration is possible but the input port
				doesn't forward any message therefore the
				output port will never have a message to drop
			\item \emph{output insertion port} ($s\dicom r$), where
				all the ouput-assertions have been inserted by
				the output port
			\item\label{drop-injection} \emph{output injection
				port}, this configuration is impossible since
				there is no Assertions from the input-port to
				inject (or it behaves as $s\dicom r$)
			\item\label{drop-seldrop} \emph{output selective drop
				port}, as in \ref{drop-injection} there is no
				Assertion from the input port therfore no
				selective port is possible in general. In this
				case this configuration is impossible or
				behaves as $s\ddcom r$
			\item \emph{output selective insertion port}, as in
				\ref{drop-seldrop} impossible, or behaves as
				$s\dicom r$
			\item \emph{output selective injection port}, as in
				\ref{drop-seldrop} impossible, or behaves as
				$s\dicom r$
			\item \emph{ouput secure port} ($s\dscom r$)
		\end{enumerate}

>>>>

\fix{mr}{this proof needs to be done. The current text
is not sufficient} 
\begin{proof}
\begin{enumerate}
	\item \emph{input secure port} and 
		\begin{enumerate}
			\item \emph{output drop port} ($s\sdcom r$), 
			\item \emph{output insertion port} ($s\sicom r$), 
			\item \emph{output injection port} ($s\sjcom r$), 
			\item \emph{output selective drop port} ($s\ssdcom r$), 
			\item \emph{output selective insertion port} ($s\ssicom r$), 
			\item \emph{output selective injection port} ($s\ssjcom r$), 
		\end{enumerate}
	\item \emph{input drop port} (all the input-assertions are dropped) and 
		\begin{enumerate}
			\item \emph{output drop port} ($s\ddcom r$), this
				configuration is possible but the input port
				doesn't forward any message therefore the
				output port will never have a message to drop
			\item \emph{output insertion port} ($s\dicom r$), where
				all the ouput-assertions have been inserted by
				the output port
			\item\label{drop-injection} \emph{output injection
				port}, this configuration is impossible since
				there is no Assertions from the input-port to
				inject (or it behaves as $s\dicom r$)
			\item\label{drop-seldrop} \emph{output selective drop
				port}, as in \ref{drop-injection} there is no
				Assertion from the input port therfore no
				selective port is possible in general. In this
				case this configuration is impossible or
				behaves as $s\ddcom r$
			\item \emph{output selective insertion port}, as in
				\ref{drop-seldrop} impossible, or behaves as
				$s\dicom r$
			\item \emph{output selective injection port}, as in
				\ref{drop-seldrop} impossible, or behaves as
				$s\dicom r$
			\item \emph{ouput secure port} ($s\dscom r$)
		\end{enumerate}

### 2020-06-09 reports/confidential/problem_statement.tex
mark white paper as confidential

%Either a valid security hypothesis can be formulated based on one or more of
%the concepts reviewed (and depicted in Figure~\ref{fig:safety-security}) or it
%can't.  Since, in the next Section, we will define our security hypothesis (on
%top of which we'll develop a security theory) on those terms, if the second case
%is true we will not formulate a valid security theory. However, while we want
%to highlight that the incompleteness of this review may be a potential issue;
%on the other hand, due to the nature of a literature review, it seems to us
%that only an inductive approach can be used and then any literature review will
%be incomplete.  If the first case applies, in one of those terms one shall find
%a valid ground on top of which formulate a security hypothesis (assuming that a
%valid security hypothesis exists).

Our literature review shows that most of the definitions relates insecurity to
dis-honesty (also called maliciousness or adversarial) of an agent (often
called adversary or attacker). We can synthesize this belief in the
following hypothesis.

\begin{hypothesis}{\bf Security as Honesty and Insecurity as Dishonesty --}
	\begin{itemize}
		\item a closed system can be considered \emph{secure} if there
			is no dishonest agent
		\item a closed system can be considered \emph{insecure} if
			there is a dishonest agent 
	\end{itemize}
	where an agent is any virtual or physical entity of the system or using
	the system (e.g. a device, a software, or a human being) and dishonesty
	is not necessarily related to malicious motivation but also to
	incompetence or lack of skills.
\end{hypothesis}
As in the Dolev-Yao theory, we may correlate ``being dishonest'' to ``not
following the intended behavior/rules''.  In the case of a generic system, a
dishonest agent is, therefore, any agent that doesn't follow the intended
behavior (or functionality or logic) of the system.  Given the generality of
the definition, and its high level of abstraction, we may
conclude that the hypothesis seems evident. For example, a software can be
considered an agent of the system and whenever it has a bug, it can be
exploited causing an Incident. However, this hypothesis has lead to the
un-testable conclusion that the dishonest behaviors of agents cannot be defined
in general (e.g. due to the heterogeneity of agents and systems) 
and that huge repository of dishonest behaviors should be kept as
definition, such as CWE\autocite{MITRE2020CWEresearch}, CVE\autocite{CVE},
CAPEC\autocite{MITRE2020CAPEC}, NVD\autocite{NIST2020NVD};
or that dishonesty of an agent with respect to a security protocol should be
defined as a number of predefined actions as in
\autocite{Turuani2006clatse,Basin2005ofmc,Armando2016satmc,Rocchetto2017interpolation}
(to name a few).

We now proceed with a more detailed analysis of the terms
and with the re-formulation of the security hypothesis.

>>>>

Our literature review shows that most of the definitions relates insecurity to
dis-honesty (also called maliciousness or adversarial) of an agent (often
called adversary or attacker). This, however, just moves the problem of
defining what cybersecurity is as the problem of defining what an dishonest
agent can or cannot do in a system\footnote{where an agent is any virtual or
physical entity of the system or using the system (e.g. a device, a software,
or a human being) and dishonesty is not necessarily related to malicious
motivation but also to incompetence or lack of skills.}
As in the Dolev-Yao theory, we may correlate ``being dishonest'' to ``not
following the intended behavior/rules''.  In the case of a generic system, a
dishonest agent is, therefore, any agent that doesn't follow the intended
behavior (or functionality or logic) of the system.  Given the generality of
the definition, and its high level of abstraction, we may
conclude that the hypothesis seems evident. For example, a software can be
considered an agent of the system and whenever it has a bug, it can be
exploited causing an Incident. However, this hypothesis has lead to the
un-testable conclusion that the dishonest behaviors of agents cannot be defined
in general (e.g. due to the heterogeneity of agents and systems) 
and that huge repository of dishonest behaviors should be kept as
definition, such as CWE\autocite{MITRE2020CWEresearch}, CVE\autocite{CVE},
CAPEC\autocite{MITRE2020CAPEC}, NVD\autocite{NIST2020NVD};
or that dishonesty of an agent with respect to a security protocol should be
defined as a number of predefined actions as in
\autocite{Turuani2006clatse,Basin2005ofmc,Armando2016satmc,Rocchetto2017interpolation}
(to name a few).
